\bf\mftitle

### 2011-01-30 doc/jInfer/twostep/twostep.tex
Documentation: TwoStep review.

%#### SUBMODULES->PassRepresentant ############################################
\subsection{PassRepresentant (ClusterProcessor)} \label{section_PassRepresentant}
Simple example to read. For each cluster return its representant as a rule to be in schema.
This has nothing to do with infering grammar, it is just proof of submodules concept.
Input documents are not valid against this odd grammar.
Do not use this in practice, just read the code to understand the bare minimum needed to implement submodule.

@@

%#### SUBMODULES->AutomatonMergingState ############################################
\subsection{AutomatonMergingState (ClusterProcessor)} \label{section_AutomatonMergingState}
\begin{figure}[tpb]
	\centering\includegraphics[scale=\myscale]{automaton_merging_state_modules}
	\caption{Submodules of AutomatonMergingState cluster processor} \label{automaton_merging_state_modules}
\end{figure}
\begin{figure}[tpb]
	\centering\includegraphics[scale=1]{automaton_merging_state_flow}
	\caption{Data flow of AutomatonMergingState cluster processor} \label{automaton_merging_state_flow}
\end{figure}
\jmodule{AutomatonMergingState} is implementation of merging state algorithm on nondeterministic finite automaton (see package \code{cz.cuni.mff.ksi.jinfer.twostep.processing.automatonmergingstate}).
\subsubsection{Structure} \label{section_AutomatonMergingState_structure}
Shortened code of cluster processor operation:
\begin{verbatim}
// 1. Construct PTA
Automaton<AbstractStructuralNode> automaton = new Automaton<AbstractStructuralNode>(true);

@@

// 3. Convert Automaton<AbstractStructuralNode> to RegexpAutomaton<AbstractStructuralNode>
RegexpAutomaton<AbstractStructuralNode> regexpAutomaton =
    new RegexpAutomaton<AbstractStructuralNode>(simplifiedAutomaton);
// 4. Call regexpAutomatonSimplifier to obtain regular expression from regexpAutomaton
Regexp<AbstractStructuralNode> regexp =
    regexpAutomatonSimplifier.simplify(regexpAutomaton, regexpAbstractToString);

// 5. Return element with regexp
return new Element(
      new ArrayList<String>(),
      rules.get(0).getName(),
      new HashMap<String, Object>(),
      regexp,
      new ArrayList<Attribute>()
      );
\end{verbatim}
The whole submodule structure is drawn on fig. \ref{automaton_merging_state_modules}.

\subsubsection{Data flow}
It works in steps:
\begin{enumerate}
	\item It creates prefix-tree automaton (PTA) from positive examples - right sides of rules given.
Then it calls its submodule called \jmodule{AutomatonSimplifier} to  modify PTA to some generalized 
automaton by merging states.
	\item Simplified automaton is then converted to an instance of \code{RegexpAutomaton} (see \ref{section_RegexpAutomaton}) by using clone constructor.
Regexp automaton is automaton with regular expression as symbol on transitions.
In automata theory, such automaton is called extended NFA.
Clone constructing is done by converting each symbol in source automaton to regexp token with that symbol as \code{content}.
	\item \code{RegexpAutomaton} is then passed into second submodule called \jmodule{RegexpAutomatonSimplifier}.
Its job is to derive regular expression from automaton, such that automaton and regular expression represents same language.
\end{enumerate}
The data flow is on fig. \ref{automaton_merging_state_flow}.

>>>>

%#### SUBMODULES->PassRepresentant ############################################
\subsection{PassRepresentant (ClusterProcessor)} \label{section_PassRepresentant}
Trivial ClusterProcessor implementation. For each cluster return its representant as the rule to be in resulting schema.
This has nothing to do with grammar simplification, it is just a proof-of-concept submodule.
Input documents are not valid against this odd grammar.
Do not use this in practice, just read the code to understand the bare minimum needed to implement a submodule.

@@

%#### SUBMODULES->AutomatonMergingState ############################################
\subsection{AutomatonMergingState (ClusterProcessor)} \label{section_AutomatonMergingState}
\begin{figure}[tpb]
	\centering\includegraphics[scale=\myscale]{automaton_merging_state_modules}
	\caption{Submodules of AutomatonMergingState cluster processor} \label{automaton_merging_state_modules}
\end{figure}
\begin{figure}[tpb]
	\centering\includegraphics[scale=1]{automaton_merging_state_flow}
	\caption{Data flow of AutomatonMergingState cluster processor} \label{automaton_merging_state_flow}
\end{figure}
\jmodule{AutomatonMergingState} is an implementation of merging state algorithm on nondeterministic finite automaton (see package \code{cz.cuni.mff.ksi.jinfer.twostep.processing.automatonmergingstate}).
\subsubsection{Structure} \label{section_AutomatonMergingState_structure}
Abridged code of cluster processor operation follows.
\begin{verbatim}
// 1. Construct PTA
Automaton<AbstractStructuralNode> automaton = new Automaton<AbstractStructuralNode>(true);

@@

// 3. Convert Automaton<AbstractStructuralNode> to RegexpAutomaton<AbstractStructuralNode>
RegexpAutomaton<AbstractStructuralNode> regexpAutomaton =
    new RegexpAutomaton<AbstractStructuralNode>(simplifiedAutomaton);

// 4. Call regexpAutomatonSimplifier to obtain regular expression from regexpAutomaton
Regexp<AbstractStructuralNode> regexp =
    regexpAutomatonSimplifier.simplify(regexpAutomaton, regexpAbstractToString);

// 5. Return element with regexp
return new Element(
      new ArrayList<String>(),
      rules.get(0).getName(),
      new HashMap<String, Object>(),
      regexp,
      new ArrayList<Attribute>()
      );
\end{verbatim}
The whole submodule structure is in fig. \ref{automaton_merging_state_modules}.

\subsubsection{Data flow}
\jmodule{AutomatonMergingState} works in following steps.
\begin{enumerate}
	\item Create prefix-tree automaton (PTA) from positive examples - right sides of rules.
Call its submodule \jmodule{AutomatonSimplifier} to modify PTA to some generalized automaton by merging states.
	\item Simplified automaton is then converted to an instance of \code{RegexpAutomaton} (see \ref{section_RegexpAutomaton}) by using clone constructor.
Regexp automaton is automaton with regular expression as symbol on transitions.
In automata theory, such automaton is called extended NFA.
Clone constructing is done by converting each symbol in source automaton to regexp token with that symbol as \code{content}.
	\item \code{RegexpAutomaton} is then passed into second submodule called \jmodule{RegexpAutomatonSimplifier}.
Its job is to derive regular expression from automaton, such that automaton and regular expression represent the same language.
\end{enumerate}
The data flow is in fig. \ref{automaton_merging_state_flow}.
